A Graph-based Framework for Coverage Analysis in Autonomous Driving

### 2025-10-18 article/article.tex
last changes
create first few embedding plots

\title{A Graph-based Framework for Coverage Analysis in Autonomous Driving}
\author{xxx}
\date{\today}

@@

\section{Implementation of Graph Embeddings for Traffic Scene Analysis}
\label{chapter:implementation_of_graph_embeddings_for_traffic_scene_analysis}

@@

@@

>>>>

\title{A Graph-based Framework for Coverage Analysis in Autonomous Driving}
\author{Thomas Mühlenstädt and Marius Bause}
\date{\today}

@@

\section{Graph Embeddings for Traffic Scene Analysis}
\label{chapter:implementation_of_graph_embeddings_for_traffic_scene_analysis}

@@

Training employed a self-supervised contrastive objective on mini-batches of 128 graphs. 
For each batch, two correlated views of every graph were created by 
perturbing continuous attributes with zero-mean Gaussian noise ($\sigma=0.1$) applied to node 
longitudinal speed and edge path length. A four-layer GINE encoder 
(hidden width 96) produced graph-level representations via the concatenation of 
mean, max, and sum pooling, followed by an embedding MLP (yielding 256-dimensional embeddings) and a projection head. The contrastive loss was a temperature-scaled cross-entropy over in-batch similarities (cosine similarity of $\ell_2$-normalized projections, temperature $\tau=0.1$), maximizing agreement of the two views of the same graph while contrasting against other graphs in the batch. Optimization used Adam with an exponentially decaying learning rate, initialized at 0.02 and multiplied by 0.75 across successive stages. 
This setup follows established practice in contrastive pretraining for GNNs \cite{hu2020strategiespretraininggraphneural} 
and is implemented using PyTorch Geometric \cite{Fey/Lenssen/2019}.

\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{plots/train_test_graph_embeddings_loss_plot.png}
\caption{Training and test loss for the graph embeddings model trained jointly on CARLA and Argoverse 2.0 data.}
\label{fig:train_test_graph_embeddings_loss_plot}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/graph_embeddings_pca_tsne_test_plot.png}
    \caption{PCA and t-SNE visualization of the embedding space for Carla and Argoverse 2.0 scenarios.}
    \label{fig:embedding_space}
\end{figure}
